Re-Allocation of Resources during Releases \titlenote{Copyright note}

### 2013-11-14 paper1/paper1.tex
minor edits to research questions

\title{Re-Allocation of Resources during Releases \titlenote{Copyright note}}
\numberofauthors{2}
\author{
% 1st. author
\alignauthor
Md Tajmilur Rahman\\
       \affaddr{Concordia University}\\
       \affaddr{Montreal, QC H3G 1M8}\\
       \affaddr{438-932-2288, +1}\\
       \email{mdt\_rahm@encs.concordia.ca}
% 2nd. author
\alignauthor
Peter C. Rigby\\
       \affaddr{Concordia University}\\
       \affaddr{Montreal, QC H3G 1M8}\\
       \affaddr{514-848-2424, +1}\\
       \email{peter.rigby@concordia.ca}
}
\date{20 Oct 2013}
\maketitle
\begin{abstract}
This section will be written at the end.
\end{abstract}
\category{K.6.3}{Software Management}{Software Development, Software Resource Management, Resource Reallocation}
\terms{Experiment, Human Factors, Resource Management, Reallocation}
\keywords{Resource Reallocation, Code Ownership, Defect Density, Software Releases} % NOT required for Proceedings
\section{Introduction}
Software projects are notorious for going over budget and schedule. Rush periods are often get seen before a major release that turn the developers into dinosaurs as Frederick Brooks likens in his benchmark study "The Mythical Man Month" \cite{brooks_mythical}. This "Rush To Release (RTR)" can be prompted either by external forces such as decisions by management to include new features in the release or to release earlier to beat a competitor. Alternatively, the rush may simply be due to inappropriate or unrealistic scheduling. Whatever the reason is it is an obvious. Regardless of the causes, the rush to release stresses developers and often requires developers to work on unusual, high priority or critical areas of the system. In this paper we study how RTR effects project organization and introduces technical debt. We want to propose a method to observe, analyze and summarize the results of revisions found near release. We intend to infer behavior of the developers related to the process around release time. The key research questions that we expect to answer with our methodology are as follows:
\begin{enumerate}
\item Do developers work on different areas of the system around the time of release?
\item Are there certain areas of the system that receive increased attention (i.e.\ do developers focus on a smaller set of files around releases)?
\item Do the areas of code that are modified around the time of release have higher defect densities than code that is modified during normal development?
\end{enumerate}

>>>>

\title{Re-Allocation of Resources during Releases \titlenote{Copyright note}}
\numberofauthors{2}
\author{
% 1st. author
\alignauthor
Md Tajmilur Rahman\\
       \affaddr{Concordia University}\\
       \affaddr{Montreal, QC H3G 1M8}\\
       \affaddr{438-932-2288, +1}\\
       \email{mdt\_rahm@encs.concordia.ca}
% 2nd. author
\alignauthor
Peter C. Rigby\\
       \affaddr{Concordia University}\\
       \affaddr{Montreal, QC H3G 1M8}\\
       \affaddr{514-848-2424, +1}\\
       \email{peter.rigby@concordia.ca}
}
\date{20 Oct 2013}
\maketitle
\begin{abstract}
This section will be written at the end.
\end{abstract}
\category{K.6.3}{Software Management}{Software Development, Software Resource Management, Resource Reallocation}
\terms{Experiment, Human Factors, Resource Management, Reallocation}
\keywords{Resource Reallocation, Code Ownership, Defect Density, Software Releases} % NOT required for Proceedings
\section{Introduction}
Software projects are notorious for going over budget and schedule. Rush periods are often get seen before a major release that turn the developers into dinosaurs as Frederick Brooks likens in his benchmark study "The Mythical Man Month" \cite{brooks_mythical}. This "Rush To Release (RTR)" can be prompted either by external forces such as decisions by management to include new features in the release or to release earlier to beat a competitor. Alternatively, the rush may simply be due to inappropriate or unrealistic scheduling. Whatever the reason is it is an obvious. Regardless of the causes, the rush to release stresses developers and often requires developers to work on unusual, high priority or critical areas of the system. In this paper we study how RTR effects project organization and introduces technical debt. We want to propose a method to observe, analyze and summarize the results of revisions found near release. We intend to infer behavior of the developers related to the process around release time. The key research questions that we expect to answer with our methodology are as follows:
\begin{enumerate}

\item What is the release process used by the project?
\item Do developers work on different areas of the system around the time of release?
\item Are there certain areas of the system that receive increased attention (i.e.\ do developers focus on a smaller set of files around releases)?
\end{enumerate}

During the merge window, developers are free to provide any change that is ready for release. During the release candinate period, we would expect to see fixs on the files that were changed during the previous merge window. We measure this by comparing the Jac of merge window with the subsequent rc period, compared with the merge window and subsequent merge window.
